High-Throughput Computing on \\ High-Performance Platforms: A Case Study

### 2017-09-10 overall.tex
minor fixes and line savings.

Initially, all the shared libraries and the python scripts of AthenaMP were
stored on the OLCF Spider 2 Lustre file system. However, the I/O patterns of
the initialization and configuration stages degraded the performance of the
filesystem. This was addressed by moving the AthenaMP distribution to a
read-only NFS directory, shared among Titan's DTNs and worker nodes. NFS
eliminated the problem of metadata contention, improving metadata read
performance from a worse case scenario of 6,300s on Lustre to \(\approx\)225s
on NFS\@. While these figures are specific to OLCF and TItan, reengineering
of AthenaMP could further improve startup time on every platform.

@@

The performance analysis of Titan's AMD CPUs for detector simulations helps
also to compare Titan and Grid site performances. Usually, Grid sites exposes
resources with heterogeneous CPU architectures and 8 (virtual) cores, while
Titan's offer an homogeneous 16 cores architecture. We used the rate of
events processes per minute as a measure of the efficiency of executing the
same detector simulation on Titan or Grid sites. Comparisons of the
efficiencies of Titan to the BNL and SIGNET Grid sites, normalized for 8
cores, show that the effective performance per-core at Titan is
\(\approx\)0.57 event per minute, roughly 1/2 of BNL and  1/3 of SIGNET
performances.

The differences in performance between Titan and the BNL and SIGNET Grid
sites are due to the FP scheduler competition but mainly to the availability
of newer processors. 
% The CPUs at the Grid sites have one FP scheduler per core and are on
% average newer than the CPU of Titan.
The heterogeneity of the Grid sites' CPUs explain the higher performance
variance we observed compared to the performance consistency we measured on
Titan. This difference in performance is compensated by the amount of
resources available on Titan (capable of executing up to 30\%/year of the
ATLAS detector simulations) and by the lack of further resources available to
WLCG\@. Also, it should be noted that Titan is at the end of its life-cycle
and that Summit, Titan's successor, will offer cutting-edge performances.

>>>>

Initially, all the shared libraries and the python scripts of AthenaMP were
stored on the OLCF Spider 2 Lustre file system. However, the I/O patterns of
the initialization and configuration stages degraded the performance of the
filesystem. This was addressed by moving the AthenaMP distribution to a
read-only NFS directory, shared among Titan's DTNs and worker nodes. NFS
eliminated the problem of metadata contention, improving metadata read
performance from a worse case scenario of 6,300s on Lustre to \(\approx\)225s
on NFS\@. While these figures are specific to OLCF and Titan, reengineering
of AthenaMP could improve startup time on every platform.

@@

A performance analysis of Titan's AMD CPUs for detector simulations also helps
to compare Titan and Grid site performance. Usually, Grid sites expose
resources with heterogeneous CPU architectures and 8 (virtual) cores, while
Titan's offer an homogeneous 16 cores architecture. We used the rate of events
processes per minute as a measure of the efficiency of executing the same
detector simulation on Titan or Grid sites. Comparisons of the efficiencies of
Titan to the BNL and SIGNET Grid sites, normalized for 8 cores, show that the
effective performance per-core at Titan is
\(\approx\)0.57 event per minute, roughly 1/2 of BNL and  1/3 of SIGNET.

%performances.

% The CPUs at the Grid sites have one FP scheduler per core and are on
% average newer than the CPU of Titan.

The differences in performance between Titan and the BNL and SIGNET Grid
sites are due to the FP scheduler competition but mainly to the availability
of newer processors. 
The heterogeneity of the Grid sites' CPUs explain the higher performance
variance we observed compared to the performance consistency we measured on
Titan. This difference in performance is compensated by the amount of
resources available on Titan (capable of executing up to 30\%/year of the
ATLAS detector simulations) and by the lack of further resources available to
WLCG\@. Also, it should be noted that Titan is at the end of its life-cycle
and that Summit, Titan's successor, will offer cutting-edge performances.
